\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-03 slides/gvn-hoist.tex
fix

\frame{\frametitle{\GVN{}-Hoist: Hoisting Computations from Branches}
  \begin{itemize}
    \item identifies identical computations in a function
    \item hoist identical computations to a common dominator
    \item reduces code size
    \item reduces critical path lenth by exposing more ILP
  \end{itemize}
}

\begin{frame}[fragile]{Example of hoisting}
  \begin{lstlisting}
  if (inv >= 0) {
    tmin = (min - a) * inv;
    tmax = (max - a) * inv;
  } else {
    tmin = (max - a) * inv;
    tmax = (min - a) * inv;
  }
  \end{lstlisting}

@@

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item compute value number of scalars, loads, stores, calls
  \item compute insertion points of each type of instructions
  \item hoist expressions
  \item propagate changes by updating SSA
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  current GVN not accurate for loads and stores:
  \begin{itemize}
  \item scalars: use the existing GVN infrastructure
  \item loads: VN the pointer operand
  \item stores: VN the pointer operand and the value being stored
  \item calls: as stores, loads, or scalars (following side effects)
  \end{itemize}
}

>>>>

\begin{frame}[fragile]{CFGSimplify limits}
  \begin{lstlisting}
  if (inv >= 0) {
    tmin = (min - a) * inv;
    tmax = (max - a) * inv;
  } else {
    tmin = (max - a) * inv;
    tmax = (min - a) * inv;
  }
  \end{lstlisting}

@@

\frame{\frametitle{\GVN{}-Hoist: Hoisting Computations from Branches}
  \begin{itemize}
    \item identifies identical computations in a function
    \item hoist identical computations to a common dominator
    \item reduces code size
    \item reduces critical path length by exposing more ILP
  \end{itemize}
}

\frame{\frametitle{Optimistic \GVN{}-hoist Algorithm}
  \begin{itemize}
  \item compute value number of scalars, loads, stores, calls
  \item compute insertion points of each type of instructions
  \item hoist expressions and propagate changes by updating SSA
  \end{itemize}
}

\begin{frame}[fragile]{Value Numbering}

  \begin{columns}[T,onlytextwidth] % align columns
    \column{.3\textwidth}
    \begin{block}{\small Simple program}
      \begin{lstlisting}
a = x + y
b = x + 1
c = y + 1
d = b + c
e = a + 2
      \end{lstlisting}
    \end{block}
    \pause
    \column{.2\textwidth}
    \begin{center}
      \vspace{1cm}
      $\rightarrow$
    \end{center}
    \column{.3\textwidth}
    \begin{block}{\small Value Numbering}
      \begin{lstlisting}
a -> 1
b -> 2
c -> 3
d -> 4
e -> 4
      \end{lstlisting}
    \end{block}
  \end{columns}

\end{frame}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  \begin{itemize}
  \item scalars: use the existing GVN infrastructure
  \item loads: VN the pointer operand
  \item stores: VN the pointer operand and the value being stored
  \item calls: as stores, loads, or scalars (following side effects)
  \end{itemize}
  current GVN not accurate for loads and stores: use ad-hoc change
}
